\sysfull

### 2018-08-07 paper/asplos19/hwswsetup.tex
Methodology revised revised

\begin{table}
	\centering
	\footnotesize
	\begin{tabular}{| r|r|r | p{0.54\columnwidth} |}
		\hline
		App.&tasks&SLOC&Description\\
		\hline\hline
        \textbf{ar} &10 &428 & activity recognition using a KNN\\ % with a deterministic input from a randomly-generated sequence of accelerometer data\\
		\hline
        \textbf{bc} &10 &371 & several bitcount algorithms\\
        % \textbf{bc} &10 &371 & Counts bits in bytes sequences
% using several algorithms and check for correctness\\
		\hline
                \textbf{cuckoo} &14 &426 & Cuckoo Filter with pseudo-random values\\
		\hline
        \textbf{dijkstra} &5 &198 & Dijkstra shortest path algorithm \\
		\hline
        \textbf{fft} &8 &449 & Fast Fourier Transform\\ % on three pre-generated 128 sample vectors\\
		\hline
		\textbf{sort} &4 &167 & selection sort algorithm\\
		\hline
	\end{tabular}
\caption{Characteristics of benchmarks used for evaluation.}
\label{table:benchmark_table}
\end{table}

>>>>

\begin{table}
	\centering
	\footnotesize
	\begin{tabular}{| r|r|r | p{0.54\columnwidth} |}
		\hline
		App.&Tasks&SLOC&Description\\
		\hline\hline
        \emph{ar} &10 &428 & activity recognition using a KNN\\ % with a deterministic input from a randomly-generated sequence of accelerometer data\\
		\hline
        \emph{bc} &10 &371 & several bitcount algorithms\\
        % \textbf{bc} &10 &371 & Counts bits in bytes sequences
% using several algorithms and check for correctness\\
		\hline
        \emph{cuckoo} &14 &426 & Cuckoo Filter with pseudo-random values\\
		\hline
        \emph{dijkstra} &5 &198 & Dijkstra shortest path algorithm \\
		\hline
        \emph{fft} &8 &449 & Fast Fourier Transform\\ % on three pre-generated 128 sample vectors\\
		\hline
		\emph{sort} &4 &167 & selection sort algorithm\\
		\hline
	\end{tabular}
\caption{Characteristics of benchmarks used for evaluation.}
\label{table:benchmark_table}
\end{table}
